Lasso_RCI_Response

### 2024-02-19 Lasso_RCI_Response.Rmd
Updated peramiters (added substance use)

          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | 
          Schiz_P == 1 |  Schizaff_P == 1,  

@@

    #OCD_Co_C = as.factor(
     # ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
    BPD_Co_C = as.factor(
      ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
    No_Co = as.factor(
      ifelse(BPD_Co_C == 0 &
               Somatic_C == 0 & 
               Eating_C == 0 &
               Psychotic_C == 0 &
               Trauma_C == 0 & 
               Substance_C == 0 &
               Mood_C == 0 &
               Anxiety_C == 0, 1,0)),
    Other_Co = as.factor(
      ifelse(  Somatic_C == 1 & 
               Eating_C == 1 &
               Psychotic_C == 1,1,0)),

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )

@@

pre-post scores by treatment response
```{r}
# Treatment scores
#1. Make DF + name columns
Scores_tab <- data.frame(matrix(nrow = 9 ,ncol=7))
colnames(Scores_tab) = c("Variables", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)")

@@

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
Vars_dep <- Mothership_post |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_anx <- Mothership_post |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

@@

predict.df <- data.frame(
  model = c("Min", "1se", "Full"),
  values = c(Mean.predict.min.dep,Mean.predict.1se.dep,Mean.predict.full.model.dep)
)
predict.df
```

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output

## min model
  glm_min_dep <-  
      glm(
      #Outcome varaible
        Depression_Responder ~ 
      # predictors
        Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
        rdq_func_change,
      #data
      data = Vars_dep, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min.dep      <- summary(glm_min_dep)

  tidy.summary.min.dep <- tidy(glm_min_dep)
tidy.summary.min
# Coefficients
  coefs.min.dep <- abs(coef(glm_min_dep))

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
        Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min.anx      <- summary(glm_min_anx)

@@

## 1se model
  glm_1se_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
         Days_not_attended_1 + rdq_coping_change + rdq_pmh_change + rdq_func_change,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.anx      <- summary(glm_1se_anx)

>>>>

          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1,

@@

    #OCD_Co_C = as.factor(
     # ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
    BPD_Co_C = as.factor(
      ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
    No_Co = as.factor(
      ifelse(BPD_Co_C == 0 &
               Somatic_C == 0 & 
               Eating_C == 0 &
               Psychotic_C == 0 &
               Trauma_C == 0 & 
               Substance_C == 0 &
               Mood_C == 0 &
               Anxiety_C == 0, 1,0)),
    Other_Co = as.factor(
      ifelse(  Somatic_C == 1 & 
               Eating_C == 1, 1,0)),

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 1 |
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )

@@

pre-post scores by treatment response - TOGETHER
```{r}
# Treatment scores
#1. Make DF + name columns
Scores_tab <- data.frame(matrix(nrow = 9 ,ncol=7))
colnames(Scores_tab) = c("Variables", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)")

@@

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
Vars_dep <- Mothership_post |>
  select( c(
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

str(Vars_dep)

Vars_anx <- Mothership_post |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

old model
# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,

@@

predict.df <- data.frame(
  model = c("Min", "1se", "Full"),
  Mean_Predict = c(Mean.predict.min.dep,Mean.predict.1se.dep,Mean.predict.full.model.dep)
)
predict.df
```

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output
# Old model
# ## min model
#   glm_min_dep <-  
#       glm(
#       #Outcome varaible
#         Depression_Responder ~ 
#       # predictors
#         Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
#         rdq_func_change,
#       #data
#       data = Vars_dep, 
#       # type of regression : logistic = binary / binomial
#       family = "binomial")
```

```{r}
## min model
  glm_min_dep <-
      glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Married + Days_not_attended_1 + Mood_D + Substance_D + Anxiety_C +
        Substance_C + CUDOS_pre + CUXOS_pre + rdq_coping_change + 
        rdq_pmh_change + rdq_func_change,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

# Summary of the model
  summary.min.dep      <- summary(glm_min_dep)
  summary.min.dep

  tidy.summary.min.dep <- tidy(glm_min_dep)

# Coefficients
  coefs.min.dep <- abs(coef(glm_min_dep))

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

@@

# Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
#         Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Married + White + Days_complete_1 + Days_not_attended_1 + 
        Anxiety_D + Mood_C + Substance_C + Trauma_C +  CUDOS_pre + CUXOS_pre + 
        rdq_coping_change + rdq_pmh_change + rdq_func_change,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min.anx      <- summary(glm_min_anx)

@@

## 1se model
  glm_1se_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
         CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.anx      <- summary(glm_1se_anx)
